Paper Figures

### 2022-03-25 03_data_viz.Rmd
add cache import

# LH-SIP data but with 3d as the starting timepoint
LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")
```

>>>>

# LH-SIP data but with 3d as the starting timepoint
LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")

# BacDive Data
bacdive_FA <- readRDS(file = "cache/bacdive_FA")
bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide")
```
